SMT-Boosted Security Types for Low-Level MPC

### 2024-10-10 esop25/cpj.tex
checkpoint

\cnote{Define (conditional) inputs in hyperproperties section.}

\begin{lemma}
  \label{lemma-eqsprogsound}
  If $\toeq{\prog} \models \eqs$ and $\eqs \models \eqs'$, then
  for all $\store \in \runs(\prog)$ we have $\store \models \eqs'$.
\end{lemma}

\begin{definition}
  \label{definition-sound}
  Given $\prog$ with $\iov(\prog) = S \cup M \cup P \cup O$
  and $\flips(\prog) = R$, we say that
  \emph{$\Gamma$ is sound for $\prog$} iff for all $M' \subseteq M$
      and $X \subseteq S \cup R$, the following
      conditions hold:
  \begin{enumerate}[\hspace{5mm}i.]
    \item  if $X$ are inputs to $M'$ then
      there exists $\ty$ with $\leakj{\Gamma}{M'}{\ty}$ and $X \subseteq \ty$.
    \item  for all  $R' \subseteq R$, if
      $X$ are $R'$ are conditional inputs to $M'$ then $\leakj{\Gamma}{M'}{\ty}$
      and $\leakclose{\Gamma}{\ty \cup R'}{\ty'}$ and $X \subseteq \ty'$.
  \end{enumerate}
\end{definition}

@@

    \eqj{R_1}{\eqs}{\toeq{\elab{\be}{\cid}}}{\ty_0}
  \end{mathpar}
  are both valid, and by the induction hypothesis $\Gamma_0$ is sound for $\prog_0$.
  We can then proceed by a second induction on the derivation of $\ty_0$, where there
  are two subcases. \cnote{complete me.}
\end{proof}

Our main type soundness result combines typing and leakage judgements,
and guarantees gradual release of protocols-- that is, that adversarial
messages reflect no dependencies on honest secrets.
\cnote{Need to define gradual release... should probably have a section
  where we summarize hyperproperties.}
\begin{theorem}
  \label{theorem-cpj}
  Given $\prog$ with $\views(\prog) = M \cup P$, if $\cpj{R}{\eqs}{\eqspre \wedge \toeq{\prog}}{\Gamma}$
  is valid and for all $H,C$ we have $\leakj{\Gamma}{M_C}{T}$ with $T$ closed
  and $S_H \cap T = \varnothing$, then $\prog$ satisfies gradual release.
\end{theorem}
\begin{proof}
  Immediate by Lemma \ref{lemma-cpjsound}. \qed
\end{proof}

>>>>

\begin{definition}
  Given $\prog$ with $\iov(\prog) = S \cup V \cup O$, we say that
  $X \subseteq S \cup \flips(\prog)$ \emph{interfere with} 
  $M \subseteq V$ iff $\progd{\prog} \not\vdash X * M$.
\end{definition}

\begin{lemma}
  Given $\prog$ with $\iov(\prog) = S \cup V \cup O$ and $\flips(\prog) = R$,
  for all $x \in S \cup R$ and $M \subseteq V$ exactly one of the following conditions holds:
  \begin{enumerate}[\hspace{5mm}i.]
  \item $\setit{x}$ interferes with $M$.
  \item There exists $X \subseteq S \cup R$ such that $\setit{x} \cup X$ interferes
    with $M$ but neither $X$ nor $\setit{x}$ alone do, in which case we say
    that $\setit{x}$ interferes with $M$ conditionally on $X$.
  \item Neither condition (i) nor (ii) hold.
  \end{enumerate}
\end{lemma}

%\begin{lemma}
%  \label{lemma-eqsprogsound}
%  If $\toeq{\prog} \models \eqs$ and $\eqs \models \eqs'$, then
%  for all $\store \in \runs(\prog)$ we have $\store \models \eqs'$.
%\end{lemma}

\begin{definition}
  \label{definition-sound}
  Given $\prog$ with $\iov(\prog) = S \cup M \cup P \cup O$
  and $\flips(\prog) = R$, we say that
  \emph{$\Gamma$ is sound for $\prog$} iff for all $M' \subseteq M$
      and $x \in S \cup R$, the following
      conditions hold:
  \begin{enumerate}[\hspace{5mm}i.]
    \item  if $\setit{x}$ interferes with $M'$ then
      there exists $\ty$ with $\leakj{\Gamma}{M'}{\ty}$ and $x \in \ty$.
    \item  if there exists  $X \subseteq S \cup R$ such that
      $\setit{x}$ interferes with $M'$ conditionally on $X$,
      then $\leakj{\Gamma}{M'}{\ty}$ and
      $\leakclose{\Gamma}{\ty \cup X}{\ty'}$ and
      $\setit{x} \in \ty'$.
  \end{enumerate}
\end{definition}

@@

    \eqj{R_1}{\eqs}{\toeq{\elab{\be}{\cid}}}{\ty_0}
  \end{mathpar}
  are both valid, and by the induction hypothesis $\Gamma_0$ is sound for $\prog_0$.
  We can then proceed by a second induction on the derivation of $\ty_0$, where there
  are two subcases defined by the $\TirName{DepTy}$ and $\TirName{Encode}$ rules.
  In the former case the result is immediate since all variables occuring in
  $\toeq{\elab{\be}{\cid}}$ are elements of $\ty_0$ by definition. In the latter case,
  we have:
  \begin{mathpar}
    \eqs \models \toeq{\elab{\be}{\cid}} \eop \phi' \fminus \rx{w}{\cid}

    \ty_0 = \cty{\rx{w}{\cid}}{\ty_1}

    R_1 = R_2;\setit{\rx{w}{\cid}}

    \eqj{R_2}{\eqs}{R_2}{\ty_1}
  \end{mathpar}
  These facts imply that $\rx{w}{\cid}$ is used as a one-time-pad to encode
  $\phi$ and introduces interference conditional on $\rx{w}{\cid}$
  \cite{barthe2019probabilistic}. Observing that:
  $$
  \leakclose{\Gamma}{\setit{\cty{\rx{w}{\cid}}{\ty_1}, \rx{w}{\cid}}}{\ty'}
  $$
  The result in this subcase follows by the (second) induction hypothesis. \qed
\end{proof}

Our main type soundness result combines typing and leakage judgements,
and guarantees gradual release of protocols-- that is, that adversarial
messages reflect no dependencies on honest secrets.
\begin{theorem}
  \label{theorem-cpj}
  Given $\prog$ with $\views(\prog) = M \cup P$, if $\cpj{R}{\eqs}{\eqspre \wedge \toeq{\prog}}{\Gamma}$
  is valid and for all $H,C$ we have $\leakj{\Gamma}{M_C}{T}$ with $T$ closed
  and $S_H \cap T = \varnothing$, then $\prog$ satisfies gradual release.
\end{theorem}
\begin{proof}
  Immediate by Lemma \ref{lemma-cpjsound}. \qed
\end{proof}
